---
title: "Noora Health - WhatsApp Norms Survey Analysis"
author: "Zezhen Wu"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
  html_document:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

# TL;DR

The survey analysis covers 770 participants across three forms (2505202343, 2505202344, 2505202350), with barrier questions asked only in forms 2505202343 and 2505202344. All figures below are aggregate percentages.

**State abbreviations**
- **PB:** Punjab  
- **KT:** Karnataka  
- **MP:** Madhya Pradesh  
- **MH:** Maharashtra  

**1. High agreement with norms messages**

- Overall agreement is very strong (> 70% across all items; most > 80%, some > 90%).  

- Cultural acquiescence to Likert scales may inflate these percentages, but we should still use them to guide message design (e.g., **94.3%** of mothers in Karnataka agree that “Doing KMC helps babies bond with their caregivers/parents”).

**2. Barrier questions and framing effects**

- Most participants report “no problem” with KMC, cord care, and diet.  

- Positively framed statements see near-universal agreement, whereas negatively framed items (e.g., “I disapprove of putting oil, powder, ghee, ash, turmeric, or cow dung on a baby’s cord”) and nuanced diet statements (“It’s good to eat all types of hot or cold food postpartum” and “Eating any type of hot or cold food won’t negatively impact mother or baby”) show greater response variability.

**3. Self-reported KMC practice vs. historical benchmarks**

- **Current self-reported KMC rate:** 51.4% overall (PB: 44.1%; KT: 49.6%; MP: 67.2%; MH: 57.9%).  

- Substantially higher than the **8.1%** reported in Subramanian et al. (2020), likely reflecting differences in KMC explanation to participants and our use of convenience sampling.  


```{r setup, include=F}
knitr::opts_chunk$set(
  dev  = "png",   # use PNG for high‐res bitmaps
  dpi  = 300,     # render at 300dpi
  fig.width = 6,   # your preferred width
  fig.height = 4,    # your preferred height
  echo=FALSE, 
  results='asis'
  )

library(tidyverse)
library(lubridate)
# library(googlesheets4)
library(scales)
library(rsurveycto)
library(knitr)
library(kableExtra)

# load data from surveycto server
auth = rsurveycto::scto_auth(here::here('secrets/scto_auth.txt'))

form_id = 'whatsapp_norms_survey'
d = scto_read(auth, form_id)
m = scto_get_form_metadata(auth, form_id)

# select usable data
dat <- d |> 
  filter(start_survey == 1) |> 
  filter(formdef_version %in% c("2505202350", "2505202341", "2505202343", "2505202344")) |> 
  filter(
    !between(
      date(starttime),
      ymd("2025-05-23"),
      ymd("2025-05-25")
    )
  )

```

```{r load google data, include=F}
# load data
# sheet_url <- "https://docs.google.com/spreadsheets/d/1zZLUIFtPDegqX1fIx96NajCS4rIs-6AnwBtK7lUtf3Q/edit?gid=870695215#gid=870695215"
# 
# sheet_names(sheet_url)
# 
# dat <- read_sheet(sheet_url, sheet = "short survey data")
```

```{r data cleaning function, include=F}
make_multiselect_dummies <- function(df, vars, sep = "\\s+") {
  # 1) add row ID
  df %>% 
    mutate(.row = row_number()) -> df_id
  
  # 2) for each variable, build its dummy block and join back
  for (var in vars) {
    df_id %>%
      transmute(.row,
                choice = str_trim(as.character(.data[[var]]))) %>%
      separate_rows(choice, sep = sep) %>%
      filter(!is.na(choice), choice != "") %>%
      mutate(present = 1) %>%
      pivot_wider(
        id_cols       = .row,
        names_from    = choice,
        values_from   = present,
        values_fill   = list(present = 0),
        names_prefix  = paste0(var, "_")
      ) -> dummies
    
    df_id <- df_id %>% left_join(dummies, by = ".row")
  }
  
  # 3) drop helper and originals
  df_id %>%
    select(-.row, -all_of(vars))
}

```

```{r data prep, include=F}
# 0) data prep

## recode multiselect variables
dat_s <- make_multiselect_dummies(
  dat,
  vars = c("reduce_diet", "kmc_prac_hard", "cord_hard", "hard_diet")
)

## select variables
dat_s <- dat_s |> 
  select(formdef_version, state, date, phn_nmbr, relation, 
         age, mthr_age, type_del, sex_baby, birth_date, first_baby, first_baby_mthr, weight, 
         highest_qual, mthr_qual, occupation_cgr, mthr_occupation, category, 
         state_resp, bpl, help_mthr, religion, # demographics
         
         kmc_perform, kmc_perform_othr, kmc_who_1, kmc_who_2, kmc_who_3, kmc_who_4, kmc_who_88, # KMC practice
         cord, cord_apply_1, cord_apply_2, cord_apply_3, cord_apply_4, cord_apply_5, cord_apply_77, cord_apply_88, # Cord care practice
         diet, diet_mthr, reduce_diet_1, reduce_diet_2, reduce_diet_3, reduce_diet_4, reduce_diet_77, reduce_diet_88, # Diet practice
         
         physcl_benefit, bond, sleep, warm, engaging, othr_parents, own, birth_wgt, sick, father_kmc, do_kmc, mothr_kmc, family_kmc, # KMC norms
         risk, avoid, best_way, wash, infection, dry, clean, disapprove, # Cord care norms
         nutritious, all_types, hotcold, variety_mthr, variety, reduce, sickfood, drink, optimise, optimise_mthr, # Diet practice
         
         kmc_prac_hard_1, kmc_prac_hard_2, kmc_prac_hard_3, kmc_prac_hard_5, kmc_prac_hard_6, 
         kmc_prac_hard_7, kmc_prac_hard_8, kmc_prac_hard_9, kmc_prac_hard_11, kmc_prac_hard_88, kmc_prac_othr, # KMC barriers
         
         cord_hard_1, cord_hard_2, cord_hard_4, cord_hard_5, cord_hard_6, cord_hard_7, cord_hard_8, cord_hard_88, cord_hard_othr, # Cord care barriers
         
         hard_diet_1, hard_diet_2, hard_diet_3, hard_diet_5, hard_diet_6, hard_diet_88, hard_diet_othr # Diet barriers
         )

# labels
belief_labs <- c(
  `1`  = "Agree",
  `0`  = "Disagree",
  `77` = "Don't know",
  `33` = "Don't want to respond"
)

yesno_labs <- c(
  `1`  = "Yes",
  `0`  = "No"
)

yesnodont1_labs <- c(
  `1`  = "Yes",
  `2`  = "No",
  `77` = "Don't know"
)

yesnodont2_labs <- c(
  `1`  = "Yes",
  `0`  = "No",
  `77` = "Don't know"
)

state_labs <- c(
  `1` = "Karnataka",
  `2` = "Madhya Pradesh",
  `3` = "Maharashtra",
  `4` = "Punjab"
)

rel_labs <- c(
  `1`  = "Mother",
  `2`  = "Father",
  `3`  = "Maternal grandmother",
  `4`  = "Paternal grandmother",
  `88` = "Other"
)

qual_labs <- c(
  `1`  = "Don't know how to read or write",
  `2`  = "Read/write but no school",
  `3`  = "Up to 5th standard",
  `4`  = "6th to 10th standard",
  `5`  = "11th to degree/diploma",
  `6`  = "Post graduate",
  `77` = "Don't know"
)

occ_labs <- c(
  `1`  = "Unemployed",
  `2`  = "Farmer",
  `3`  = "Homemaker",
  `4`  = "Self employed / small business",
  `5`  = "Daily labourer",
  `6`  = "Private job",
  `7`  = "Public sector job",
  `77` = "Don't know"
)

type_del_labs <- c(
  `1` = "Normal",
  `2` = "C‐section"
)

sex_labs <- c(
  `1` = "Male",
  `2` = "Female"
)

cat_labs <- c(
  `1`  = "General",
  `2`  = "SC/ST/OBC",
  `77` = "Don't know / no response",
  `88` = "Other"
)

state_resp_labs <- c(
  `1`  = "Karnataka",
  `2`  = "Punjab",
  `3`  = "Maharashtra",
  `4`  = "Madhya Pradesh",
  `88` = "Other: Specify"
)

religion_labs <- c(
  `1`  = "Hinduism",
  `2`  = "Islam",
  `3`  = "Jainism",
  `4`  = "Sikhism",
  `5`  = "Buddhism",
  `6`  = "Christianity",
  `77` = "Prefer not to say",
  `88` = "Other"
)

# 3) apply in one mutate
dat_s <- dat_s %>%
  mutate(
    # state & relation
    state    = recode(state,  !!!state_labs),
    relation = recode(relation, !!!rel_labs),

    # simple yes/no/dk
    across(c(diet_mthr, first_baby, first_baby_mthr, kmc_who_1:kmc_who_88, reduce_diet_1:reduce_diet_88, cord_apply_1:cord_apply_77, kmc_prac_hard_1:hard_diet_88),
           ~ recode(.x, !!!yesno_labs)),

    # binary 1/0 → Yes/No
    across(c(bpl, cord, diet),  ~ recode(.x, !!!yesnodont1_labs)),
    across(c(kmc_perform, kmc_perform_othr),  ~ recode(.x, !!!yesnodont2_labs)),

    # beliefs: KMC, cord‐care & diet beliefs
    across(c(physcl_benefit:optimise_mthr), ~ recode(.x, !!!belief_labs)),

    # delivery & baby
    type_del = recode(type_del, !!!type_del_labs),
    sex_baby = recode(sex_baby, !!!sex_labs),

    # education & occupation
    across(c(highest_qual, mthr_qual), ~ recode(.x, !!!qual_labs)),
    across(c(occupation_cgr, mthr_occupation), ~ recode(.x, !!!occ_labs)),

    # category & religion
    category = recode(category, !!!cat_labs),
    religion = recode(religion, !!!religion_labs),
    
    # state of the respondent
    state_resp = recode(state_resp,   !!!state_resp_labs)
    
  )


# Merge mutually exclusive questions separated for mothers and other respondents
dat_s <- dat_s %>%
  mutate(
    first_baby_mother = case_when(
      relation == "Mother" & !is.na(first_baby)      ~ first_baby,
      relation != "Mother" & !is.na(first_baby_mthr) ~ first_baby_mthr,
      TRUE                                            ~ NA_character_
    )) |> 
   mutate(
    diet_mother = case_when(
      relation == "Mother" & !is.na(diet_mthr)      ~ diet_mthr,
      relation != "Mother" & !is.na(diet) ~ diet,
      TRUE                                            ~ NA_character_
    )) |> 
  mutate(
    variety_mother = case_when(
      relation == "Mother" & !is.na(variety_mthr)      ~ variety_mthr,
      relation != "Mother" & !is.na(variety) ~ variety,
      TRUE                                            ~ NA_character_
    )) |> 
  mutate(
    optimise_mother = case_when(
      relation == "Mother" & !is.na(optimise_mthr)      ~ optimise_mthr,
      relation != "Mother" & !is.na(optimise) ~ optimise,
      TRUE                                            ~ NA_character_
    )) |> 
  mutate(
    age_mother = case_when(
      relation == "Mother" & !is.na(age)      ~ age,
      relation != "Mother" & !is.na(mthr_age) ~ mthr_age,
      TRUE                                            ~ NA_character_
    )) |> 
  mutate(
    highest_qual_mother = case_when(
      relation == "Mother" & !is.na(highest_qual)      ~ highest_qual,
      relation != "Mother" & !is.na(mthr_qual) ~ mthr_qual,
      TRUE                                            ~ NA_character_
    )) |> 
  mutate(
    occupation_mother = case_when(
      relation == "Mother" & !is.na(occupation_cgr)      ~ occupation_cgr,
      relation != "Mother" & !is.na(mthr_occupation) ~ mthr_occupation,
      TRUE                                            ~ NA_character_
    ))

# recode numeric variables
dat_s <- dat_s |> 
  mutate(across(c(help_mthr, weight, age_mother), as.numeric))


```

```{r variable labels, include=F}
var_labels_df <- data.frame(name = names(dat_s)) |> 
  left_join(m[[8]][[6]] |> select(name, `label:English`), by = "name") |> 
  rename(description = `label:English`)

var_labels_df <- var_labels_df |> 
  mutate(
    description = case_when(
      name == "kmc_who_1" ~ "Who did this care? - Mother",
      name == "kmc_who_2" ~ "Who did this care? - Father",
      name == "kmc_who_3" ~ "Who did this care? - Maternal grandmother",
      name == "kmc_who_4" ~ "Who did this care? - Paternal grandmother",
      name == "kmc_who_88" ~ "Who did this care? - Other",
      
      name == "cord_apply_1" ~ "What did you put on the baby’s cord? - Talcum/babyPowder",
      name == "cord_apply_2" ~ "What did you put on the baby’s cord? - Oil or ghee",
      name == "cord_apply_3" ~ "What did you put on the baby’s cord? - Blue medicine",
      name == "cord_apply_4" ~ "What did you put on the baby’s cord? - Betadine (Surgical powder or medicine)",
      name == "cord_apply_5" ~ "What did you put on the baby’s cord? - Turmeric powder/oil with turmeric powder",
      name == "cord_apply_77" ~ "What did you put on the baby’s cord? - Don’t Know",
      name == "cord_apply_88" ~ "What did you put on the baby’s cord? - Other",
      
      name == "reduce_diet_1" ~ "What did you reduce or eliminate in the diet? - Yogurt",
      name == "reduce_diet_2" ~ "What did you reduce or eliminate in the diet? - Citrus fruits",
      name == "reduce_diet_3" ~ "What did you reduce or eliminate in the diet? - Non-vegetarian food",
      name == "reduce_diet_4" ~ "What did you reduce or eliminate in the diet? - Lentils",
      name == "reduce_diet_77" ~ "What did you reduce or eliminate in the diet? - Don’t Know",
      name == "reduce_diet_88" ~ "What did you reduce or eliminate in the diet? - Other",
      
      name == "kmc_prac_hard_1"  ~ "What made it hard to practice KMC? - People think KMC is only for weak or small babies",
      name == "kmc_prac_hard_2"  ~ "What made it hard to practice KMC? - Mothers feel shy or uncomfortable opening their clothes",
      name == "kmc_prac_hard_3"  ~ "What made it hard to practice KMC? - Family elders say it's not needed",
      name == "kmc_prac_hard_5"  ~ "What made it hard to practice KMC? - Mothers are in pain or tired after delivery",
      name == "kmc_prac_hard_6"  ~ "What made it hard to practice KMC? - Lack of privacy at home",
      name == "kmc_prac_hard_7"  ~ "What made it hard to practice KMC? - Families don’t understand KMC properly during the hospital session",
      name == "kmc_prac_hard_8"  ~ "What made it hard to practice KMC? - Families don’t feel confident in doing KMC at home",
      name == "kmc_prac_hard_9"  ~ "What made it hard to practice KMC? - Families forgot or didn’t think it was important",
      name == "kmc_prac_hard_11" ~ "What made it hard to practice KMC? - Mothers are expected to help others, but feel uncomfortable asking for help with KMC",
      name == "kmc_prac_hard_88" ~ "What made it hard to practice KMC? - Other (please type)",

      name == "cord_hard_1"  ~ "What made it hard to practice dry cord care? - Family elders said to apply oil, powder, or home remedies",
      name == "cord_hard_2"  ~ "What made it hard to practice dry cord care? - Parents and caregivers are not convinced that dry cord care is enough",
      name == "cord_hard_4"  ~ "What made it hard to practice dry cord care? - Parents and caregivers are concerned that others would judge them for engaging in dry cord care",
      name == "cord_hard_5"  ~ "What made it hard to practice dry cord care? - They do not understand how to take care of the cord",
      name == "cord_hard_6"  ~ "What made it hard to practice dry cord care? - They thought applying oil or powder would help with healing or preventing infections",
      name == "cord_hard_7"  ~ "What made it hard to practice dry cord care? - The hospital did not explain cord care clearly",
      name == "cord_hard_8"  ~ "What made it hard to practice dry cord care? - They forgot what was said in the hospital session",
      name == "cord_hard_88" ~ "What made it hard to practice dry cord care? - Other (please type)",
      
      name == "hard_diet_1"  ~ "What made it hard to eat a nutritious diet? - Family elders do not believe mothers should be eating certain foods post-delivery",
      name == "hard_diet_2"  ~ "What made it hard to eat a nutritious diet? - They were told to avoid cold, spicy, or hard foods",
      name == "hard_diet_3"  ~ "What made it hard to eat a nutritious diet? - Mother was not allowed to eat enough or certain foods or water by her family members, even if she prepared the food at home",
      name == "hard_diet_5"  ~ "What made it hard to eat a nutritious diet? - The hospital session said not to restrict food intake, but we don’t believe that’s the right approach",
      name == "hard_diet_6"  ~ "What made it hard to eat a nutritious diet? - We were afraid it would harm the baby or the mother (e.g., gas, pain, cold)",
      name == "hard_diet_88" ~ "What made it hard to eat a nutritious diet? - Other (please type)",
      
      name == "first_baby_mother" ~ "Is this mother's first baby?",
      name == "diet_mother" ~ "Since the baby was born, has the mother reduced or eliminated anything in her diet (food or water)?",
      name == "variety_mother" ~ "“I do my best to (help the mother) eat a variety of nutritious foods and avoid restricting her diet after delivery.”",
      name == "optimise_mother" ~ "“I try to (make sure the mother) drink(s) at least 2 liters (or 8–10 glasses) of water a day to support healthy milk production.”",
      name == "age_mother" ~ "What is baby's mother's age?",
      name == "highest_qual_mother" ~ "What is mother’s highest educatio",
      name == "occupation_mother" ~ "What is the mother’s occupation?",
      TRUE ~ description
    )
  )

var_labels <- setNames(var_labels_df$description, var_labels_df$name)

```

```{r table function, include=F}
# Table Function

summarize_question_by_state <- function(df, state_var, response_var, title) {
  # map full state names to abbreviations
  abbr_map <- c(
    "Punjab"         = "PB",
    "Karnataka"      = "KT",
    "Madhya Pradesh" = "MP",
    "Maharashtra"    = "MH",
    "Other, Specify" = "Other"
  )
  
  # 1) Normalize NA into "Missing" and count by state & response
  df2 <- df %>%
    mutate(
      response = ifelse(
        is.na(.data[[response_var]]),
        "Missing",
        as.character(.data[[response_var]])
      )
    ) %>%
    count(
      state    = .data[[state_var]],
      response
    ) %>%
    group_by(state) %>%
    mutate(percent = n / sum(n) * 100) %>%
    ungroup()
  
  # 2) Wide table of "N (P%)" per state
  wide_states <- df2 %>%
    mutate(label = paste0(n, " (", round(percent, 1), "%)")) %>%
    select(response, state, label) %>%
    pivot_wider(
      names_from  = state,
      values_from = label,
      values_fill = "0 (0.0%)"
    )
  
  # 3) Total column "N (P%)" out of overall total
  total <- df2 %>%
    group_by(response) %>%
    summarise(n_total = sum(n), .groups = "drop") %>%
    mutate(
      pct_total = n_total / sum(n_total) * 100,
      Total     = paste0(n_total, " (", round(pct_total, 1), "%)")
    ) %>%
    select(response, Total)
  
  # 4) Join & rename state columns to PB/KT/MP/MH/Other
  result <- wide_states %>%
    left_join(total, by = "response") %>%
    rename_with(~ abbr_map[.x], intersect(names(abbr_map), names(.))) %>%
    select(response, any_of(c("PB","KT","MP","MH","Other")), Total)
  
  # 5) Rank the responses by Total count
  result <- result %>%
  mutate(
    Total_count = as.integer(str_extract(Total, "^[0-9]+")),
    is_missing  = response == "Missing"
  ) %>%
  arrange(desc(!is_missing), desc(Total_count)) %>%  # Prioritize non-missing, then missing, then count
  select(-Total_count, -is_missing)
  
  # 6) Build the Grand Total row (including Missing in state counts)
  totals_by_state <- df2 %>%
    group_by(state) %>%
    summarise(n = sum(n), .groups = "drop")
  
  total_respondents <- sum(totals_by_state$n)
  
  grand_labels <- totals_by_state %>%
    mutate(
      abbr  = abbr_map[state],
      label = paste0(n, " (", round(n / total_respondents * 100, 1), "%)")
    ) %>%
    select(abbr, label) %>%
    pivot_wider(names_from = abbr, values_from = label)
  
  grand_row <- grand_labels %>%
    mutate(
      response = "Total",
      Total    = paste0(total_respondents, " (100.0%)")
    ) %>%
    select(names(result))

  # 7) bind and return
  df_tab <- bind_rows(result, grand_row)
  
  names(df_tab)[1] <- title
  
  return(df_tab)
    
}


summarize_question <- function(df, var) {
  # Ensure the variable is a symbol
  var <- rlang::ensym(var)
  
  # Count values and calculate percentage
  summary_tbl <- df %>%
    dplyr::count(!!var) %>%
    dplyr::mutate(
      percent = n / sum(n),
      formatted = paste0(n, " (", sprintf("%.1f%%", percent * 100), ")")
    ) %>%
    dplyr::select(!!var, formatted)
  
  # Add Total row
  total_n <- sum(df %>% dplyr::count(!!var) %>% dplyr::pull(n))
  total_row <- tibble::tibble(
    !!var := "Total",
    formatted = paste0(total_n, " (100.0%)")
  )
  
  # Combine
  final_tbl <- dplyr::bind_rows(summary_tbl, total_row)
  
  return(final_tbl)
}

summary_cont_question <- function(df, state_var, response_var, digits = 2) {
  df %>%
    # 1) group by the column whose name is in `state_var`
    group_by_at(vars(all_of(state_var))) %>%
    # 2) compute mean & SD of the column named in `response_var`
    summarise(
      mean_val = mean(.data[[response_var]], na.rm = TRUE),
      sd_val   = sd(.data[[response_var]],   na.rm = TRUE),
      .groups  = "drop"
    ) %>%
    # 3) glue them into "M = xx (SD = xx)"
    mutate(
      summary = sprintf(
        paste0("M = %.", digits, "f (SD = %.", digits, "f)"),
        mean_val, sd_val
      )
    ) %>%
    # 4) keep only the grouping column + our formatted summary
    select(all_of(state_var), summary) %>%
    # 5) pivot so each state becomes its own column
    pivot_wider(
      names_from  = all_of(state_var),
      values_from = "summary"
    )
}

summary_multiselect_by_state <- function(df, state_var, vars, title, digits = 1) {
  tbl <- df %>%
    # 1) Per‐state respondent count and per‐var 1‐counts
    group_by(across(all_of(state_var))) %>%
    summarise(
      n_resp = n(),
      across(
        all_of(vars),
        ~ sum(. == "Yes", na.rm = TRUE),
        .names = "count_{.col}"
      ),
      .groups = "drop"
    ) %>%
    
    # 2) Pivot to long so we can compute percentages
    pivot_longer(
      cols      = starts_with("count_"),
      names_to  = "name",
      values_to = "count",
      names_prefix = "count_"
    ) %>%
    
    # 3) % within each state
    mutate(
      percent = count / n_resp * 100,
      summary = sprintf(
        paste0("%d (%.", digits, "f%%)"),
        count, percent
      )
    ) %>%
    
    # 4) Drop intermediate columns and spread back out
    select(-count, -n_resp, -percent) %>%
    pivot_wider(
      names_from  = all_of(state_var),
      values_from = summary
    ) %>%
    
    # 5) Attach your label lookup and reorder
    left_join(var_labels_df, by = "name") %>%
    select(description, everything(), -name)
  
  # 6) Rename the first column
  names(tbl)[1] <- title
  tbl
}

print_tab <- function(tbl){
  
    if (!is.null(knitr::pandoc_to()) && knitr::pandoc_to() == "docx") {
      # Word output: use pandoc table
      print(
        kable(
          tbl,
          format  = "pandoc",
          caption = title
        )
      )
    } else {
      # HTML/PDF/Console: styled striped table
      print(
        kable(
          tbl,
          format     = "html",
          table.attr = "class='table table-striped'",
          align      = rep("l", ncol(tbl))
        )
      )
    }
  
  # small gap before the next one
  cat("\n\n")
  
}
```

```{r figure function, include=F}
plot_hist <- function(df, var, label, binwidth = 1) {
  vals     <- df[[var]]
  n_total  <- sum(!is.na(vals))
  mean_val <- mean(vals, na.rm = TRUE)
  sd_val   <- sd(vals, na.rm = TRUE)

  # get max count for padding
  h <- hist(
    vals,
    breaks = seq(
      min(vals, na.rm = TRUE) - 0.5,
      max(vals, na.rm = TRUE) + 0.5,
      by = binwidth
    ),
    plot = FALSE
  )
  y_max <- max(h$counts)

  ggplot(df, aes(x = .data[[var]])) +
    # counts histogram
    geom_histogram(
      aes(y = after_stat(count)),
      binwidth = binwidth,
      fill     = "steelblue",
      alpha    = 0.6,
      color    = "white"
    ) +
    # density curve scaled to counts
    geom_density(
      aes(y = after_stat(density * n_total * binwidth)),
      color = "darkblue",
      size  = 1
    ) +
    # red mean line
    geom_vline(
      xintercept = mean_val,
      color      = "red",
      linetype   = "dashed",
      size       = 1
    ) +
    # annotate mean & SD
    annotate(
      "text",
      x     = mean_val,
      y     = y_max * 1.05,
      label = paste0("M = ", round(mean_val, 1), 
                     "; SD = ", round(sd_val, 1)),
      hjust = 0.5,
      vjust = 0
    ) +
    # pad y‐axis for text
    scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
    labs(
      title = label,
      x     = label,
      y     = "Count"
    ) +
    theme_minimal()
}

plot_density <- function(df, var, label, adjust = 1) {
  vals     <- df[[var]]
  mean_val <- mean(vals, na.rm = TRUE)
  sd_val   <- sd(vals, na.rm = TRUE)

  ggplot(df, aes(x = .data[[var]])) + 
    # smooth density curve
    geom_density(
      color  = "darkblue",
      fill   = "steelblue",
      alpha  = 0.5,
      adjust = adjust
    ) +
    # red dashed mean line
    geom_vline(
      xintercept = mean_val,
      color      = "red",
      linetype   = "dashed",
      size       = 1
    ) +
    # annotation for mean & SD just above the curve
    annotate(
      "text",
      x     = mean_val,
      y     = Inf,
      label = paste0("M = ", round(mean_val, 1),
                     "; SD = ", round(sd_val, 1)),
      vjust = 2,
      hjust = 0.5,
      color = "black"
    ) +
    labs(
      title = label,
      x     = label,
      y     = "Density"
    ) +
    theme_minimal()
}

```

# 1. Summary Tables for Demographic Questions

```{r state}
response_var = "state"
title = var_labels[response_var]
    
cat("### ", title, "\n\n")

tbl <- summarize_question(dat_s, "state")
names(tbl) <- c("State", "Count (Percentage)")  

print_tab(tbl)
```

```{r relation}
response_var = "relation"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r age}
response_var = "age_mother"
title = var_labels[response_var]
    
cat("### ", title, "\n\n")

tbl <- summary_cont_question(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var)

print_tab(tbl)
```

```{r type_del}
response_var = "type_del"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r sex_baby}
response_var = "sex_baby"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r first_baby}
response_var = "first_baby_mother"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r weight}
response_var = "weight"
title = var_labels[response_var]
    
cat("### ", title, "\n\n")

tbl <- summary_cont_question(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var)

print_tab(tbl)
```

```{r highest_qual_mother}
response_var = "highest_qual_mother"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s |> filter(relation == "Mother"), 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r highest_qual}
response_var = "highest_qual"
title = var_labels[response_var]

cat("### ", title, "(answered by respondents who are not the mother)", "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s |> filter(relation != "Mother"), 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r occupation_mother}
response_var = "occupation_mother"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s |> filter(relation == "Mother"), 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r occupation_cgr}
response_var = "occupation_cgr"
title = var_labels[response_var]

cat("### ", title, "(answered by respondents who are not the mother)", "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s |> filter(relation != "Mother"), 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r category}
response_var = "category"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r bpl}
response_var = "bpl"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r help_mthr}
response_var = "help_mthr"
title = var_labels[response_var]
    
cat("### ", title, "\n\n")

tbl <- summary_cont_question(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var)

print_tab(tbl)
```

```{r religion}
response_var = "religion"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

# 2. Summary Tables for Health Practices

```{r kmc_perform}
response_var = "kmc_perform"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r kmc_perform_othr}
response_var = "kmc_perform_othr"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r kmc_who}
response_var = grep("^kmc_who_", names(dat_s), value = TRUE)
title = "Who did this care?"

cat("### ", title, "(among those who answer yes to the previous question)", "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s |> filter(kmc_perform == "Yes"), 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

```{r cord}
response_var = "cord"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r cord_apply}
response_var = grep("^cord_apply_", names(dat_s), value = TRUE)
title = "What did you put on the baby’s cord?"

cat("### ", title, "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s, 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

```{r diet_mother}
response_var = "diet_mother"
title = var_labels[response_var]

cat("### ", title, "\n\n")

tbl <- summarize_question_by_state(
  df = dat_s, 
  state_var = "state", 
  response_var = response_var, 
  title = title)

print_tab(tbl)
```

```{r reduce_diet}
response_var = grep("^reduce_diet", names(dat_s), value = TRUE)
title = "What did you reduce or eliminate in the diet?"

cat("### ", title, "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s, 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

# 3. Summary Tables for Norms Questions

```{r norms}
# 1) build a character vector of your vars:
response_vars <- names(dat_s |> select(physcl_benefit:family_kmc))

# 2) loop:
for (response_var in response_vars) {
  
  # pull the human‐readable title from your var_labels vector
  title <- var_labels[response_var]
  
  # print a section header
  cat("### ", title, "\n\n")
  
  # run your summary function
  tbl <- summarize_question_by_state(
    df           = dat_s,
    state_var    = "state",
    response_var = response_var,
    title        = title
  )
  
  # print the result
  print_tab(tbl)
  
  # optional line‐break between tables
  cat("\n\n")
}

```

# 4. Summary Tables for Barriers Questions

```{r, include = F}
dat_s_short <- dat_s |> filter(formdef_version %in% c("2505202343", "2505202344"))
```

```{r barriers}
# 1) build a character vector of your vars:
response_vars <- names(dat_s_short |>
                                  select(risk:drink, 
                                         -variety_mthr, diet_mother, 
                                         variety_mother, optimise_mother) 
                       )

# 2) loop:
for (response_var in response_vars) {
  
  # pull the human‐readable title from your var_labels vector
  title <- var_labels[response_var]
  
  # print a section header
  cat("### ", title, "\n\n")
  
  # run your summary function
  tbl <- summarize_question_by_state(
    df           = dat_s_short,
    state_var    = "state",
    response_var = response_var,
    title        = title
  )
  
  # print the result
  print_tab(tbl)
  
  # optional line‐break between tables
  cat("\n\n")
}

```

```{r kmc_prac_hard}
response_var = grep("^kmc_prac_hard_", names(dat_s_short), value = TRUE)
title = "What do you think makes it hard for families to practice KMC at home?"

cat("### ", title, "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s_short, 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

**While many people selected "Other", most of them answered "No Problem."**

```{r kmc_prac_othr}
tbl <- as.data.frame(unique(dat_s_short$kmc_prac_othr))
title <- "Please tell us briefly what else makes it hard to do KMC."
names(tbl) <- title

cat("### ", title, "\n\n")

print_tab(tbl)
```

```{r cord_hard}
response_var = grep("^cord_hard_", names(dat_s_short), value = TRUE)
title = "What do you think makes it hard for families to follow dry cord care at home?"

cat("### ", title, "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s_short, 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

```{r cord_hard_othr}
tbl <- as.data.frame(unique(dat_s_short$cord_hard_othr))
title <- "Please tell us briefly what else makes it hard to do dry cord care."
names(tbl) <- title

cat("### ", title, "\n\n")

print_tab(tbl)
```

```{r hard_diet}
response_var = grep("^hard_diet_", names(dat_s_short), value = TRUE)
title = "What do you think makes it hard for mothers to eat a full and balanced diet after delivery?"

cat("### ", title, "\n\n")

tbl <- summary_multiselect_by_state(
  df = dat_s_short, 
  state_var = "state", 
  vars = response_var, 
  title = title)

print_tab(tbl)
```

```{r hard_diet_othr}
tbl <- as.data.frame(unique(dat_s_short$hard_diet_othr))
title <- "Please tell us briefly what else makes it hard for mothers to eat a healthy diet."
names(tbl) <- title

cat("### ", title, "\n\n")

print_tab(tbl)
```